Program Mutation is Just Program Transformation: \\ A Universal Approach to Mutant Generation

### 2023-03-25 paper/main.tex
Remove redundant column
Lowercase JAVA
add mean, median, std dev for valid/invalid tables
add tables for rust

% ---------------- JAVA table --------------------------
\begin{table}[hbtp]
\centering
\caption{JAVA (Regex vs. Comby)}
\label{tab:table_java1}
\resizebox{\columnwidth}{!}{%

\begin{tabular}{|c|c|c|c|c|c|}
\hline
 &  & \textbf{Valid} & \textbf{Invalid} & \textbf{Redundant} & \textbf{Valid \%}  \\ \hline
\multirow{2}{*}{pebble} & Regex & 86 & 928 & 0 & 8.48\%  \\\cline{2-6}
    & Comby & 85 & 667 & 0 & 11.30\% \\ \hline
\multirow{2}{*}{spring-hateoas} & Regex & 248 & 2231 & 0 & 10.00\% \\\cline{2-6}
    & Comby & 176 & 1212 & 0 & 12.68\% \\ \hline
\multirow{2}{*}{javacc} & Regex & 542 & 1346 & 0 & 28.70\% \\\cline{2-6}
    & Comby & 503 & 782 & 0 & 39.14\% \\ \hline
\multirow{2}{*}{coffee-gb} & Regex & 224 & 1703 & 0 & 11.63\% \\\cline{2-6}
    & Comby & 174 & 624 & 0 & 21.80\% \\ \hline
\multirow{2}{*}{egads} & Regex & 624 & 1830 & 0 & 25.43\% \\\cline{2-6}
    & Comby & 622 & 566 & 0 & 52.36\% \\ \hline
\multirow{2}{*}{apk-parser} & Regex & 351 & 1232 & 0 & 22.17\% \\\cline{2-6}
    & Comby & 338 & 866 & 0 & 28.07\% \\ \hline

@@

% ---------------- Python table --------------------------

@@

\begin{tabular}{|c|c|c|c|c|c|}
\hline
 &  & \textbf{Valid} & \textbf{Invalid} & \textbf{Redundant} & \textbf{Valid \%}  \\ \hline
\multirow{2}{*}{keract} & Comby & 1655 & 1600 &	729 & 41.53\%  \\\cline{2-6}
    & Comby & 1471 & 1063 & 533 & 47.96\% \\ \hline
\multirow{2}{*}{dtw} & Comby & 973 & 566 & 567 & 46.20\% \\\cline{2-6}
    & Comby & 866 & 330 & 639 &	47.19\% \\ \hline
\multirow{2}{*}{notion-sdk-py} & Comby & 196 & 760 & 82 & 18.89\% \\\cline{2-6}
    & Comby & 196 & 701 & 122 & 19.23\% \\ \hline

\multirow{2}{*}{atlassian-python-api} & Comby & 302	& 1002 & 207 &	19.99\% \\\cline{2-6}
    & Comby & 333 & 635 & 351 & 25.25\% \\ \hline
\multirow{2}{*}{ESD} & Comby & 1859	& 2767 & 1642 & 29.46\% \\\cline{2-6}
    & Comby & 1712 & 1548 &	614 & 44.18\% \\ \hline
\multirow{2}{*}{fiber} & Comby & 493 & 909 & 163 & 31.08\% \\\cline{2-6}
    & Comby & 458 & 767	& 241 & 31.24\% \\ \hline

@@

% ---------------- JAVA table --------------------------

\begin{table}[htbp]
\centering
\caption{JAVA (UniversalMutator vs. PIT vs. LittleDarwin)}
\label{tab:table_java2}
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|c|}
\hline
 &  & \textbf{Killed} & \textbf{Not Killed} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{Equivalent \%} \\ \hline

 \multirow{4}{*}{\small pebble} & Regex & 70 & 16 & 0.81 & - \\\cline{2-6}
    & Comby & 68 & 17 & 0.80 & - \\\cline{2-6}
    & PIT & 19 & 1 & 0.95 & - \\ \cline{2-6}
    & LittleDarwin & 8 & 0 & 1.00 & - \\ \hline
\multirow{3}{*}{\small spring-hateoas} & Regex & 82 & 166 & 0.33 & - \\\cline{2-6}
    & Comby & 65 & 111 & 0.37 & - \\ \cline{2-6}
    & PIT & 82 & 32 & 0.28 & - \\ \cline{2-6}
    & LittleDarwin & 15 & 23 & 0.39 & - \\ \hline
\multirow{3}{*}{\small javacc} & Regex & 123 & 419 & 0.23 & - \\\cline{2-6}
    & Comby & 103 & 400 & 0.21 & - \\ \cline{2-6}
    & PIT & 30 & 113 & 0.21 & -\\ \cline{2-6}
    & LittleDarwin & 64 & 18 & 0.78 & - \\ \hline
\multirow{3}{*}{\small coffee-gb} & Regex & 48 & 176 & 0.21 & - \\\cline{2-6}
    & Comby & 40 & 134 & 0.23 & - \\ \cline{2-6}
    & PIT & 32 & 4 & 0.89 & - \\ \cline{2-6}
    & LittleDarwin & 11 & 18 & 0.38 & -\\ \hline
\multirow{3}{*}{\small egads} & Regex & 442 & 182 & 0.71 & - \\\cline{2-6}
    & Comby & 422 & 200 & 0.68 & - \\ \cline{2-6}
    & PIT & 87 & 20 & 0.81 & - \\ \cline{2-6}
    & LittleDarwin & 74 & 11 & 0.87 & - \\ \hline
\multirow{3}{*}{\small apk-parser} & Regex & 26 & 325 & 0.07 & \\\cline{2-6}
    & Comby & 26 & 312 & 0.08 & -\\ \cline{2-6}
    & PIT & 14 & 75  & 0.16 & -\\ \cline{2-6}
    & LittleDarwin & 3 & 30 & 0.09 & -\\ \hline

\multirow{12}{*}{Overall} & \multirow{3}{*}{Regex} & \multicolumn{2}{c|}{Mean} & 0.39  & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.28 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.27 & - \\\cline{2-6}

 & \multirow{3}{*}{Comby} & \multicolumn{2}{c|}{Mean} & 0.40 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.30 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.26 & - \\\cline{2-6}

 & \multirow{3}{*}{PIT} & \multicolumn{2}{c|}{Mean} & 0.55 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.55 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.34 & - \\\cline{2-6}

 & \multirow{3}{*}{LittleDarwin} & \multicolumn{2}{c|}{Mean} & 0.59 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.59 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.32 & - \\ \hline

@@

% ----------------  Python table -------------------------------

@@

\multirow{3}{*}{\makecell{\small atlassian-python \\ api}} & Regex & 193 & 109 & 0.64 & - \\\cline{2-6}
    & Comby & 207 & 126 & 0.62 & - \\ \cline{2-6}
    & Mutmut & 123 & 51 & 0.71 & - \\ \cline{2-6}
    & CosmicRay & 78 & 28 & 0.74 & - \\ \hline
\multirow{3}{*}{\small ESD} & Regex & 132 & 1727 & 0.07 & - \\\cline{2-6}
    & Comby & 121 & 1591 & 0.07 & - \\ \cline{2-6}
    & Mutmut & (57+0) & 663 & 0.08 & - \\ \cline{2-6}
    & CosmicRay & 63 & 950 & 0.06 & - \\ \hline
\multirow{3}{*}{\small fiber} & Regex & 307 & 186 & 0.62 & \\\cline{2-6}
    & Comby & 291 & 167 & 0.64 & -\\ \cline{2-6}
    & Mutmut & 127 & 95 & 0.57 & -\\ \cline{2-6}
    & CosmicRay & 259 & 61 & 0.81 & -\\ \hline

\multirow{12}{*}{Overall} & \multirow{3}{*}{Regex} & \multicolumn{2}{c|}{Mean} & 0.45  & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.55 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.21 & - \\\cline{2-6}

 & \multirow{3}{*}{Comby} & \multicolumn{2}{c|}{Mean} & 0.46 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.58 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.22 & - \\\cline{2-6}

 & \multirow{3}{*}{Mutmut} & \multicolumn{2}{c|}{Mean} & 0.53 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.61 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.22 & - \\\cline{2-6}

 & \multirow{3}{*}{CosmicRay} & \multicolumn{2}{c|}{Mean} & 0.46 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.45 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.26 & - \\ \hline

>>>>

% ---------------- JAVA table UM Only--------------------------
\begin{table}[hbtp]
\centering
\caption{Java (Regex vs. Comby)}
\label{tab:table_java1}
\resizebox{\columnwidth}{!}{%

\begin{tabular}{|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c|}{} & \textbf{Valid} & \textbf{Invalid} & \textbf{Valid \%}  \\ \hline
\multirow{2}{*}{pebble} & \multicolumn{2}{c|}{Regex} & 86 & 928 & 8.48\%  \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 85 & 667 & 11.30\% \\ \hline
\multirow{2}{*}{spring-hateoas} & \multicolumn{2}{c|}{Regex} & 248 & 2231 & 10.00\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 172 & 1212 & 12.43\% \\ \hline
\multirow{2}{*}{javacc} & \multicolumn{2}{c|}{Regex} & 542 & 1346 & 28.70\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 494 & 782 & 38.71\% \\ \hline

\multirow{2}{*}{coffee-gb} & \multicolumn{2}{c|}{Regex} & 224 & 1703 & 11.63\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 174 & 624 & 21.80\% \\ \hline
\multirow{2}{*}{egads} & \multicolumn{2}{c|}{Regex} & 624 & 1830 & 25.43\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 597 & 566 & 51.33\% \\ \hline
\multirow{2}{*}{apk-parser} & \multicolumn{2}{c|}{Regex} & 351 & 1232 & 22.17\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 333 & 866 & 27.77\% \\ \hline

\multirow{6}{*}{Overall} & \multirow{3}{*}{Regex} & Mean & 345.83 & 1545.00  & 17.74\%\\\cline{3-6}
    &   &  Median & 299.50 & 1524.50 & 16.90\%  \\\cline{3-6}
    &   &  Std. Dev & 203.86 & 467.98 & 8.73\%  \\\cline{2-6}

 & \multirow{3}{*}{Comby} & Mean & 309.17 & 786.17 & 27.22\% \\\cline{3-6}
    &   &  Median & 253.50 & 724.50 & 24.79\%  \\\cline{3-6}
    &   &  Std. Dev & 202.44 & 235.24  & 15.59\%  \\\hline

@@

% ---------------- Python table UM Only --------------------------

@@

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c|}{} & \textbf{Valid} & \textbf{Invalid} & \textbf{Redundant} & \textbf{Valid \%}  \\ \hline
\multirow{2}{*}{keract} & \multicolumn{2}{c|}{Regex} & 1655 & 1600 &	729 & 41.53\%  \\\cline{2-7}
    & \multicolumn{2}{c|}{Comby} & 1471 & 1063 & 533 & 47.96\% \\ \hline
\multirow{2}{*}{dtw} & \multicolumn{2}{c|}{Regex} & 973 & 566 & 567 & 46.20\% \\\cline{2-7}
    & \multicolumn{2}{c|}{Comby} & 866 & 330 & 639 &	47.19\% \\ \hline
\multirow{2}{*}{notion-sdk-py} & \multicolumn{2}{c|}{Regex} & 196 & 760 & 82 & 18.89\% \\\cline{2-7}
    & \multicolumn{2}{c|}{Comby} & 196 & 701 & 122 & 19.23\% \\ \hline

\multirow{2}{*}{{\makecell{atlassian-python \\ api}}} & \multicolumn{2}{c|}{Regex} & 302	& 1002 & 207 &	19.99\% \\\cline{2-7}
    & \multicolumn{2}{c|}{Comby} & 333 & 635 & 351 & 25.25\% \\ \hline
\multirow{2}{*}{ESD} & \multicolumn{2}{c|}{Regex} & 1859	& 2767 & 1642 & 29.46\% \\\cline{2-7}
    & \multicolumn{2}{c|}{Comby} & 1712 & 1548 &	614 & 44.18\% \\ \hline
\multirow{2}{*}{fiber} & \multicolumn{2}{c|}{Regex} & 493 & 909 & 163 & 31.08\% \\\cline{2-7}
    & \multicolumn{2}{c|}{Comby} & 458 & 767	& 241 & 31.24\% \\ \hline

\multirow{6}{*}{Overall} & \multirow{3}{*}{Regex} & Mean & 913.00 & 1267.33 & 565.00 & 31.19\%   \\\cline{3-7}
    &   &  Median & 733.00 & 955.50 & 387.00 & 30.27\%  \\\cline{3-7}
    &   &  Std. Dev & 708.93 & 813.35 & 584.79 & 11.06\%  \\\cline{2-7}

 & \multirow{3}{*}{Comby} & Mean & 839.33 & 840.67 & 416.67 & 35.84\% \\\cline{3-7}
    &   &  Median & 662.00 & 734.00 & 442.00 & 37.71\%  \\\cline{3-7}
    &   &  Std. Dev & 628.79 & 418.99 & 211.62 & 12.28\%  \\\hline

% ---------------- Rust table UM Only --------------------------
\begin{table}[hbtp]
\centering
\caption{Rust (Regex vs. Comby)}
\label{tab:table_rust1}
\resizebox{\columnwidth}{!}{%

\begin{tabular}{|c|c|c|c|c|c|}
\hline
 & \multicolumn{2}{c|}{} & \textbf{Valid} & \textbf{Invalid} & \textbf{Valid \%}  \\ \hline
\multirow{2}{*}{cargo release} & \multicolumn{2}{c|}{Regex} & 851 &	1163 & 42.25\%  \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 1690 & 711 & 70.39\% \\ \hline
\multirow{2}{*}{passerine} & \multicolumn{2}{c|}{Regex} & 213 & 2081 & 9.29\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 173 & 1518 & 10.23\% \\ \hline
\multirow{2}{*}{typos} & \multicolumn{2}{c|}{Regex} & 386 & 1534 & 20.10\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 366 & 1199 &	 23.39\% \\ \hline

\multirow{2}{*}{ord} & \multicolumn{2}{c|}{Regex} & 762	& 2096 & 26.66\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 643 & 1669 & 27.81\% \\ \hline
\multirow{2}{*}{bazuka} & \multicolumn{2}{c|}{Regex} & 451 & 1103 & 29.02\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 402 & 920 & 30.41\% \\ \hline
\multirow{2}{*}{strum} & \multicolumn{2}{c|}{Regex} & 51 & 377	& 11.92\% \\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 50 & 318	& 13.51\% \\ \hline

\multirow{6}{*}{Overall} & \multirow{3}{*}{Regex} & Mean & 452.33 & 1392.33	& 23.21\%\\\cline{3-6}
    &   &  Median & 418.50 & 1348.50 & 23.38\%  \\\cline{3-6}
    &   &  Std. Dev & 309.05 & 656.76 & 12.16\%  \\\cline{2-6}

 & \multirow{3}{*}{Comby} & Mean & 554.00 & 1055.83	& 29.29\% \\\cline{3-6}
    &   &  Median & 384.00 & 1059.50	& 25.60\%  \\\cline{3-6}
    &   &  Std. Dev & 592.63 & 508.30 & 21.63\%  \\\hline

@@

% ---------------- JAVA table (UM vs Others) --------------------------

\begin{table}[htbp]
\centering
\caption{Java (UniversalMutator vs. PIT vs. LittleDarwin)}
\label{tab:table_java2}
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|c|}
\hline
 &  & \textbf{Killed} & \textbf{Not Killed} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{Equivalent \%} \\ \hline

 \multirow{4}{*}{\small pebble} & Regex & 70 & 16 & 0.81 & - \\\cline{2-6}
    & Comby & 68 & 17 & 0.80 & - \\\cline{2-6}
    & PIT & 19 & 1 & 0.95 & - \\ \cline{2-6}
    & LittleDarwin & 8 & 0 & 1.00 & - \\ \hline
\multirow{4}{*}{\small spring-hateoas} & Regex & 82 & 166 & 0.33 & - \\\cline{2-6}
    & Comby & 65 & 111 & 0.37 & - \\ \cline{2-6}
    & PIT & 82 & 32 & 0.28 & - \\ \cline{2-6}
    & LittleDarwin & 15 & 23 & 0.39 & - \\ \hline
\multirow{4}{*}{\small javacc} & Regex & 123 & 419 & 0.23 & - \\\cline{2-6}
    & Comby & 103 & 400 & 0.21 & - \\ \cline{2-6}
    & PIT & 30 & 113 & 0.21 & -\\ \cline{2-6}
    & LittleDarwin & 64 & 18 & 0.78 & - \\ \hline
\multirow{4}{*}{\small coffee-gb} & Regex & 48 & 176 & 0.21 & - \\\cline{2-6}
    & Comby & 40 & 134 & 0.23 & - \\ \cline{2-6}
    & PIT & 32 & 4 & 0.89 & - \\ \cline{2-6}
    & LittleDarwin & 11 & 18 & 0.38 & -\\ \hline
\multirow{4}{*}{\small egads} & Regex & 442 & 182 & 0.71 & - \\\cline{2-6}
    & Comby & 422 & 200 & 0.71 & - \\ \cline{2-6}
    & PIT & 87 & 20 & 0.81 & - \\ \cline{2-6}
    & LittleDarwin & 74 & 11 & 0.87 & - \\ \hline
\multirow{4}{*}{\small apk-parser} & Regex & 26 & 325 & 0.07 & \\\cline{2-6}
    & Comby & 26 & 312 & 0.08 & -\\ \cline{2-6}
    & PIT & 14 & 75  & 0.16 & -\\ \cline{2-6}
    & LittleDarwin & 3 & 30 & 0.09 & -\\ \hline

\multirow{12}{*}{Overall} & \multirow{3}{*}{Regex} & \multicolumn{2}{c|}{Mean} & 0.39  & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.28 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.30 & - \\\cline{2-6}

 & \multirow{3}{*}{Comby} & \multicolumn{2}{c|}{Mean} & 0.40 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.30 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.29 & - \\\cline{2-6}

 & \multirow{3}{*}{PIT} & \multicolumn{2}{c|}{Mean} & 0.55 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.55 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.37 & - \\\cline{2-6}

 & \multirow{3}{*}{LittleDarwin} & \multicolumn{2}{c|}{Mean} & 0.59 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.59 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.35 & - \\ \hline

@@

% ----------------  Python table (UM vs Others) -------------------------------

@@

\multirow{3}{*}{\makecell{\small atlassian-python \\ api}} & Regex & 193 & 109 & 0.64 & - \\\cline{2-6}
    & Comby & 207 & 126 & 0.62 & - \\ \cline{2-6}
    & Mutmut & 123 & 51 & 0.71 & - \\ \cline{2-6}
    & CosmicRay & 78 & 28 & 0.74 & - \\ \hline
\multirow{3}{*}{\small ESD} & Regex & 132 & 1727 & 0.07 & - \\\cline{2-6}
    & Comby & 121 & 1591 & 0.07 & - \\ \cline{2-6}
    & Mutmut & 57 & 663 & 0.08 & - \\ \cline{2-6}
    & CosmicRay & 63 & 950 & 0.06 & - \\ \hline
\multirow{3}{*}{\small fiber} & Regex & 307 & 186 & 0.62 & \\\cline{2-6}
    & Comby & 291 & 167 & 0.64 & -\\ \cline{2-6}
    & Mutmut & 127 & 95 & 0.57 & -\\ \cline{2-6}
    & CosmicRay & 259 & 61 & 0.81 & -\\ \hline

\multirow{12}{*}{Overall} & \multirow{3}{*}{Regex} & \multicolumn{2}{c|}{Mean} & 0.45  & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.55 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.23 & - \\\cline{2-6}

 & \multirow{3}{*}{Comby} & \multicolumn{2}{c|}{Mean} & 0.46 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.58 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.24 & - \\\cline{2-6}

 & \multirow{3}{*}{Mutmut} & \multicolumn{2}{c|}{Mean} & 0.53 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.61 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.24 & - \\\cline{2-6}

 & \multirow{3}{*}{CosmicRay} & \multicolumn{2}{c|}{Mean} & 0.46 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.45 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.28 & - \\ \hline

% ---------------- Rust table (UM vs Others)--------------------------

\begin{table}[htbp]
\centering
\caption{Rust (UniversalMutator vs. Cargo-Mutants)}
\label{tab:table_rust2}
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|c|}
\hline
 &  & \textbf{Killed} & \textbf{Not Killed} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{Equivalent \%} \\ \hline

 \multirow{3}{*}{\small cargo release} & Regex & 721 & 130 & 0.85 & - \\\cline{2-6}
    & Comby & 1344 & 346 & 0.80 & - \\\cline{2-6}
    & Cargo-Mutants & 2	& 3 & 0.40 & - \\ \hline
\multirow{3}{*}{\small passerine} & Regex & 122 & 91 & 0.57 & - \\\cline{2-6}
    & Comby & 90 & 83 & 0.52 & - \\ \cline{2-6}
    & Cargo-Mutants & 0	& 0 & 0 & - \\ \hline
\multirow{3}{*}{\small typos} & Regex & 295 & 91 & 0.76 & - \\\cline{2-6}
    & Comby & 283 & 83 & 0.77 & - \\ \cline{2-6}
    & Cargo-Mutants & 5 & 1 & 0.83 & -\\ \hline

\multirow{3}{*}{\small ord} & Regex & 558 & 204 & 0.73 & - \\\cline{2-6}
    & Comby & 533 & 110 & 0.83 & - \\ \cline{2-6}
    & Cargo-Mutants & 6 & 0 & 1.00 & - \\ \hline
\multirow{3}{*}{\small bazuka} & Regex & 281 & 170 & 0.62 & - \\\cline{2-6}
    & Comby & 291 & 111 & 0.73 & - \\ \cline{2-6}
    & Cargo-Mutants & 0 & 0 & 0 & - \\ \hline
\multirow{3}{*}{\small strum} & Regex & 8 & 43 & 0.16 & \\\cline{2-6}
    & Comby & 11 & 39 & 0.22 & -\\ \cline{2-6}
    & Cargo-Mutants & 2 & 0 & 1.00 & -\\ \hline

\multirow{9}{*}{Overall} & \multirow{3}{*}{Regex} & \multicolumn{2}{c|}{Mean} & 0.62  & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.68 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.24 & - \\\cline{2-6}

 & \multirow{3}{*}{Comby} & \multicolumn{2}{c|}{Mean} & 0.64 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.75 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.25 & - \\\cline{2-6}

 & \multirow{3}{*}{Cargo-Mutants} & \multicolumn{2}{c|}{Mean} & 0.54 & -\\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Median} & 0.62 & - \\\cline{3-6}
    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.47 & - \\ \hline
